Towards Accelerating Deep Neural Network Training on FPGAs: Facilitating the Use of Variable Precision\\ \Large{(Unrefereed Workshop Manuscript)}

### 2018-07-04 SWoPP2018 Paper/paper.tex
Fixed paragraphing issue.

The used example networks are multi-layer perceptrons (MLPs).
This means that all layers are arrays of neurons and every neuron is connected to every neuron in the next layer.
These layers are often called ``Dense'' layers.
The first data set used was MNIST~\cite{lecun2010mnist}, MNIST is a collection of 28\(\times\)28 gray scale images of hand written arabic numerals.
So the data set provides \num{784} inputs.
The structure of the sample MNIST network is shown in \cref{fig:mnist-network}.
In total a three layer network plus the input layer, or three sets of weight matrices and bias vectors.
The data set was trained using the first \num{60000} images from the MNIST data set.
The last \num{10000} images are used as the test data set.\\
The second data set used was CIFAR-10~\cite{krizhevsky2014cifar}, CIFAR-10 is a collection of 32\(\times\)32 color images divided into 10 classes, providing \num{3072} inputs.
The structure of the sample CIFAR-10 network is shown in \cref{fig:cifar10-network}.\\
The data set was trained using the first \num{50000} images from the data set.
The last \num{10000} images were used as the test data set.
All training was done using a batch size of \num{128}.
We implemented the CPU code based on NumPy's array.dot function.

>>>>

The used example networks are multi-layer perceptrons (MLPs).
This means that all layers are arrays of neurons and every neuron is connected to every neuron in the next layer.
These layers are often called ``Dense'' layers.
The first data set used was MNIST~\cite{lecun2010mnist}, MNIST is a collection of 28\(\times\)28 gray scale images of hand written arabic numerals.
So the data set provides \num{784} inputs.
The structure of the sample MNIST network is shown in \cref{fig:mnist-network}.
In total a three layer network plus the input layer, or three sets of weight matrices and bias vectors.
The data set was trained using the first \num{60000} images from the MNIST data set.
The last \num{10000} images are used as the test data set.

The second data set used was CIFAR-10~\cite{krizhevsky2014cifar}, CIFAR-10 is a collection of 32\(\times\)32 color images divided into 10 classes, providing \num{3072} inputs.
The structure of the sample CIFAR-10 network is shown in \cref{fig:cifar10-network}.
The data set was trained using the first \num{50000} images from the data set.
The last \num{10000} images were used as the test data set.
All training was done using a batch size of \num{128}.
We implemented the CPU code based on NumPy's array.dot function.
